---
title: "Biostat Method Rec 1"
author: "HS"
date: "9/10/2019"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(arsenal)
library(dplyr)
library(goeveg)
library(readxl)
#Define get mode function 
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

# Create the vector with numbers.
#v <- c(2,1,2,3,1,2,3,4,1,5,5,3,2,3)

# Calculate the mode using the user function.
#result <- getmode(v)
#print(result)

# Create the vector with characters.
#charv <- c("o","it","the","it","it")

# Calculate the mode using the user function.
#result <- getmode(charv)
#print(result)


```
## Problem 1


## Problem 2
Twenty-five randomly selected appendectomies lasted for the following lengths of time. Construct a histogram from the following data:
113 118
138 139 157 157
121 123 126 128 130 135 136 137 140 140 142 142 142 142 143 155 158 159 164

```{r problem 2}
timelength_appendectomies = c(113,118,
138, 139, 157, 157,121, 123, 126, 128, 130, 135, 136, 137, 140, 140, 142, 142, 142, 142, 143, 155, 158, 159, 164)

#Use break to set cat width
hist(timelength_appendectomies , 
     main = "Problem 2 Histogram",
     breaks = 5,
     xlab = "time length appendectomies",
     ylab = "Abundance", 
     col = "blue")

```

## Problem 3

Heart rates for ten asthmatic patients in a state of respiratory arrest are given below. Find the mean, median, and mode.

165 145 115 110 150 145 38 140 122 155

  a. What are the mean, median, and mode?

```{r cars problem 3a, echo=FALSE}
Heart_rates_asthmatic_patients = c(165,145,115,110,150,145,38,140,122,155)
mode(Heart_rates_asthmatic_patients)
fns_Heart_rates_asthmatic_patients <- fivenum(x=Heart_rates_asthmatic_patients)
```
The mean is `r mean(Heart_rates_asthmatic_patients) `

The mode is `r getmode(Heart_rates_asthmatic_patients) `

The median is `r median(Heart_rates_asthmatic_patients) `

  b. What is the five-number summary? Make a box-plot using this data. 
The five-number summary is `r fns_Heart_rates_asthmatic_patients `
```{r Boxplot of 3c}
boxplot(Heart_rates_asthmatic_patients, 
        xlab = "Heart_rates_asthmatic_patients", 
        main = "boxplot for problem 3"  )
```

  c. What is the Range:
The range is`r range(Heart_rates_asthmatic_patients)`

  d.What is the variance? Standard deviation? IQR? 
The variance is `r var(Heart_rates_asthmatic_patients)`
The SD is `r sd(Heart_rates_asthmatic_patients)`
The IQR is  `r IQR(Heart_rates_asthmatic_patients)`

  e.What is the coefficient of variation? 
The coefficient of is `r cv(Heart_rates_asthmatic_patients)`



## Problem 4
 a.For each variable (other than ID), obtain appropriate descriptive statistics (both numeric and graphic). 
##First do the continiouse variable, make a table for these
##Then do the 
```{r}
FEV_DAT <- read_excel("/Users/haosun/Desktop/Columbia\ class/P8130\ -\ BIOSTATISTICAL\ METHODS\ I/Recitation/Rec1/FEV.DAT.xls")

print("the mean is")
sapply(select(FEV_DAT,2:4), function(x) mean(as.numeric(x))) 

print("the mode is")
sapply(select(FEV_DAT,2:4), function(x) getmode(as.numeric(x))) 

print("the five number stat is")
sapply(select(FEV_DAT,2:4), function(x) fivenum(as.numeric(x))) 


print("the variance is")
sapply(select(FEV_DAT,2:4), function(x) var(as.numeric(x))) 

print("the sd is")
sapply(select(FEV_DAT,2:4), function(x) sd(as.numeric(x))) 


print("the iqr is")
sapply(select(FEV_DAT,2:4), function(x) IQR(as.numeric(x))) 

print("the coef of var is")
sapply(select(FEV_DAT,2:4), function(x) cv(as.numeric(x))) 
boxplot(select(FEV_DAT,2:4), 
        data=FEV_DAT, 
        xlab = colnames(select(FEV_DAT,2:6)), 
        main = "Boxplot for Q4a" )
```
 
 2.24 Use both numeric and graphic measures to assess the relationship of FEB to age, height, and smoking status. (Do this separately for boys and girls.) 

(Use Scaltter plot to illustrate the relationship btw continious variable)


Relationship to Smoking

```{r}
boxplot(FEV~Smoke, FEV_DAT, col=c("blue","red"))
```

Relationship to age




2.25:
Creat regressio line for the FEV and Age for boy and girls

b


```{r}
?read_excel()
rm(list=ls())

```










