---
title: "RMD for git"
author: "HS"
date: "9/12/2019"
output: html_document
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

The chunk below creates a dataframe containing a sample of size 500 from a 
random normal variable and the absolute value of each element of that sample, 
and produces a histogram of the absolute value.

```{r learning_assessment_1}
library(tidyverse)

la_df = tibble(
  norm_samp = rnorm(500),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

* The mean of the sample is `r mean(pulld(ls_df, norm_samp))`
* The median of the sample is `r median(pull(ls_df, norm_samp))`
* The median of the sample is `r median(pull(ls_df, norm_samp))`

###Scalttor plot

```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to examine a few data types (or data classes) in R.

First we create a dataframe containing variables of four different types.

```{r}
example_df = tibble(
  vec_numeric = 5:8,
  vec_char = c("My", "name", "is", "Jeff"),
  vec_logical = c(TRUE, TRUE, TRUE, FALSE),
  vec_factor = factor(c("male", "male", "female", "female"))
)
```

The variable `vec_numeric` has class `r class(pull(example_df, vec_numeric))`, and the variable `vec_factor` has class `r class(pull(example_df, vec_factor))`.
And here’s one for basic plots:

---
title: "Basic Plots"
author: "Jeff Goldsmith"
date: 2019-09-10
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to present a couple of basic plots using `ggplot`.

First we create a dataframe containing variables for our plots.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This is the change the shall be add on the example rmd

